Probe or Wait: Handling tail losses using Multipath TCP

### 2017-04-27 main.tex
Update

\begin{figure}[!ht]
\begin{center}
\includegraphics[angle=0, width=0.46\textwidth]{images/timingER3.pdf}
\end{center}
\caption{Timing diagram of MPTCP behavior with proposed improvements with loss of a) Single packet b) Two packets c) Single packet and probe loss}\label{timingNew}
\end{figure}

@@

Results comparing the burst completion time for new MPTCP TLP with that of TCP and MPTCP TLP for the considered cases are provided in 
Figure~\ref{mpnew}. In Figure~\ref{1pn}, MPTCP-New performs better than TCP in all scenarios, performs equal to MPTCP in symmetric scenarios and 
performs better than MPTCP in asymmetric scenarios with a lower delay on the alternate path. This improvement is for the reason that MPTCP-New 
allows the packet to be retransmitted on the alternate path much before the RTO. In two packet tail loss scenario as in Figure~\ref{2pn}, MPTCP-New
performs better than TCP in all scenarios and better than MPTCP in all scenarios except when the alternate path has a significantly higher delay 
than the original path, where performance is the same. In the single packet together with probe loss scenario as in Figure~\ref{1ppn}, MPTCP-New 
performs better than both MPTCP and TCP in all scenarios with PTO triggering the probe retransmission on alternate path much earlier than the RTO.

>>>>

\begin{figure*}[!ht]
\begin{center}
\includegraphics[angle=0, width=\textwidth]{images/timingER3NewTLP1.pdf}
\end{center}
\caption{Timing diagram of MPTCP behavior with proposed improvements with loss of a) Single packet b) Two packets c) Single packet and probe loss}\label{timingNew}
\end{figure*}

@@

Results comparing the burst completion time for new MPTCP TLP with that of TCP and MPTCP TLP for the considered cases are provided in 
Figure~\ref{mpnew}. In Figure~\ref{1pn}, MPTCP-New performs better than TCP in all scenarios, performs equal to MPTCP in symmetric scenarios and 
performs better than MPTCP in asymmetric scenarios with a lower delay on the alternate path. MPTCP-New achieves this improvement by retransmitting
 lost packets on the alternate path much before the RTO. In two packet tail loss scenario as in Figure~\ref{2pn}, MPTCP-New
performs better than TCP in all scenarios and better than MPTCP in all scenarios except when the alternate path has a significantly higher delay 
than the original path, where performance is the same. In the single packet together with probe loss scenario as in Figure~\ref{1ppn}, MPTCP-New 
performs better than both MPTCP and TCP in all scenarios with PTO triggering the probe retransmission on alternate path much earlier than the RTO.
